### 2025-04-18 mycv/cv_latex.tex
updates

        \section{Misc.}
        \begin{twocolentry}{2023-present}
          \begin{highlights}
          \item Board member of Korean Society for Technology of Plasticity
          \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \begin{twocolentry}{2019-present}
          \begin{highlights}
          \item Editoiral board member of Korean Journal of Metals and Materials
          \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \newpage
        \section{Full list of publications}
        \begin{enumerate}
        \item
          \begin{twocolentry}{submitted}
            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        %\begin{onecolentry}
        %    {\it }
        %\end{onecolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}

>>>>

        \section{Misc.}
        \begin{twocolentry}{2023-present}
          \begin{highlights}
          \item Board member of Korean Society for Technology of Plasticity
          \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \begin{twocolentry}{2019-present}
          \begin{highlights}
          \item Editoiral board member of Korean Journal of Metals and Materials
          \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \newpage
        \section{Full list of publications}
        \begin{enumerate}

        \item
          \begin{twocolentry}{in preparation}
            \href{}{Deformation mechanism and texture evolution in AZ31 Mg alloy under uniaxial compression: experiments and simulations}
          \end{twocolentry}
          \begin{onecolentry}
            Jongbin Go*,  {\underline{\textit{Y. Jeong}*}}, Myeong-heom Park*, Sangwon Lee, Si Gao, Nobuhiro Tsuji
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{in preparation}
            \href{}{Reverse engineering material behavior using Bayesian inference and finite element analysis on ring-pull test}
          \end{twocolentry}
          \begin{onecolentry}
            B. Jeon, C. N. Tome, P. M. Beck, B. Eftinik, A. Talapatra, {\underline{\textit{Y. Jeong}*}}, L. Capolungo*
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{submitted}
            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}
